---
output:
  md_document:
    variant: markdown_github
---

# Purpose

The purpose of this project is to practice how to make a personal project and then commit and push it onto Github. Purely for enrichment and honing the skills to work dynamically with R and cloud code storing.

In this particular exercise, I will be using Quarterly sales data to fit two model:
  -- 1: SES model
-- 2: Holt Linear Model
Then obtain each models Means Error(ME), Mean Average Error(MAE), Mean Average Prediction Error(MAPE), Mean Square Error(MSE) and their Theil's U statistics. Lastly I will plot the models together with their forecasts. 


```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
library(readxl)
```


# Loading the Data

```{r}
Quarter_sales_data <- read_excel("data/Quarter sales data.xlsx")
sales <- Quarter_sales_data[,-1]
head(Quarter_sales_data)
```

# Simple Exponential Smoothing (SES) Method

Without taking into account that we don't know the clear trends and seasonality of the sales data, the SES will be the first model we fit.

```{r}


# Fitting the SES
SES.Sales<-HoltWinters(ts(sales), beta=FALSE,gamma=FALSE)
SES.Sales

SES_Ft<-SES.Sales$fitted[,1]
SES_Ft
SES.Sales$x

error <- sales[2:24,] -as.numeric(SES_Ft)

#--------------------------------------------------------------------
E <- SES.Sales$x - SES.Sales$fitted[,1]

# Calculating Model statitics
ME_ses = mean(E[9:23,])
MAE_ses <- mean(abs(E[9:23,]))
MAPE_ses <- mean(abs(E[9:23,]/ SES.Sales$x[10:24,] )) * 100
MSE_ses <- mean(E[9:23,]^2)

A <- sum((SES_Ft[8:23]- SES.Sales$x[9:24,]/SES.Sales$x[9:24,])^2)





B <- sum((SES.Sales$x[10:24,]-SES.Sales$x[9:23,]/SES.Sales$x[9:23,])^2)

U_SES  <- sqrt(A/B)


Performance_SES <- data.frame("ME"=ME_ses, "MAE"= MAE_ses, "MAPE"= MAPE_ses,
                               "MSE"= MSE_ses, "Theil-U"= U_SES)

Performance_SES

forecast_ses <- predict(SES.Sales,n.ahead = 8)
```

